%-------------------------------------------------------------------------------
%  SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}

%-------------------------------------------------------------------------------
%  CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

  %---------------------------------------------------------
  \cventry%
  {Staff Software Engineer} % Job title
  {Ginkgo Bioworks: Biosecurity} % Organization
  {Boston, Massachusetts} % Location
  {March 2021 \-- November 2025} % Date(s)
  {%
    \begin{cvsentence}Tech lead for the software team behind a
      HIPAA-compliant pathogen surveillance platform \-- initially
      for COVID-19 in K-12 classrooms, then multipathogen
      biosurveillance across 11 international airports (126 origin countries covered). 15M+ samples
      processed, \$733M revenue.
    \end{cvsentence}
    \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Led a multi-year platform evolution from single-pathogen
        COVID testing to multipathogen biosurveillance \-- refactoring
        live production systems while preserving historical data,
      existing visualizations, and CDC reporting pipelines.}
    \item {Designed the Results \& Sample Refactor: decomposed a
        monolithic data entity into three domain objects (sample,
        procedure, result) with one-to-many relationships \-- enabling
      multi-panel testing without combinatorial data duplication.}
    \item {Grew from senior IC to de facto team lead for a team of
        \textasciitilde 11 \-- running ceremonies, managing
        stakeholders, and shielding the team from organizational churn.
        Transitioned to a traditional tech lead role when a dedicated
      manager was hired.}
    \item {DevOps: rebuilt CI/CD pipelines around Docker with GitHub
        Actions, codified infrastructure in Terraform (Auth0, AWS, Aptible,
        supporting services), migrated off legacy vendor systems, and
      achieved 8x build performance on self-hosted runners.}
    \item {Designed PHI removal from the platform as the business
        shifted from individual diagnostics to aggregate
        biosurveillance \-- balancing regulatory compliance, data
      retention, and system simplification.}
    \end{cvitems}
  }
  \begin{cventryskills}
  \item Flask
  \item SQLAlchemy
  \item PostgreSQL
  \item Terraform
  \item GitHub Actions
  \item Docker
  \item Nix
  \item AWS EC2/S3/CloudFront
  \item Auth0
  \item Aptible
  \item Grafana
  \item New Relic
  \item Heap
  \end{cventryskills}

  %---------------------------------------------------------
  \cventry%
  {Senior Software Engineer} % Job title
  {Oliver Wyman: Digital} % Organization
  {Boston, Massachusetts} % Location
  {October 2017 \-- February 2021} % Date(s)
  {%
    \begin{cvsentence}Oliver Wyman is a consulting company, where I
      had the opportunity to work across a broad range of projects
      and roles. Some highlights below:
    \end{cvsentence}
    \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {DevOps: wrote idiomatic containers, stood up many projects
        with CI/CD into Kubernetes. Member of Special Interest Group to
      spread best practices.} \\
      Synthesized an analytics stack to give consulting teams a
      platform for development, workflow scheduling, data operations,
      and execution.
    \item {Webservices: primarily backends for analytics and database
      operations, interfaced with as REST and GraphQL API services.} \\
      Developed a system that continuously collects \& collates data
      on all of Digital projects/assets \-- providing InfoSec
      auditability, surfacing lost items, and decreasing seek time
      for the Sustaining organization.
    \item {Data infrastructure: built tooling for consultants to use
        in ETL, workflow automation, schema management, and
      computational scaling.} \\
      Built out a migration-based schema framework for a project with
      a major grocery retailer, eliminating database down-time.
    \item {Sustaining: lead long-term operations for five projects in
      the mature phase of their lifecycle.}
    \end{cvitems}
  }
  \begin{cventryskills}
  \item Python
  \item Kubernetes \& Kustomize
  \item Jenkins Pipelines
  \item Prefect
  \item Node.js (Express \& Vue)
  \item Flask
  \item Alembic
  \item MS SQL Server
  \item PostgreSQL
  \item GraphQL
  \end{cventryskills}

  %---------------------------------------------------------
  \cventry%
  {Software Engineer \-- Orion: NASA's next manned spacecraft} % Job title
  {Lockheed Martin: Space Systems} % Organization
  {Littleton, Colorado} % Location
  {September 2014 \-- September 2017} % Date(s)
  {%
    \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Principal architect in moving Orion ground software from
        pen and paper to full test automation, empowering NASA
      requirement verification.}
    \item {Built a Python/LaTeX-based engine for creating NASA
        deliverables, cutting months of paperwork for engineers (per
      deliverable) to a day.}
    \item {Served as a subject matter expert for the flight software
        verification automation tiger team, sharing processes
      established while automating ground.}
    \item {Built a recursive-descent compiler for a templating
      language similar to Jinja2.}
    \item {Volunteer for Code Quest, Lockheed Martin's computer
      programming competition for high school teams.}
    \end{cvitems}
  }
  \begin{cventryskills}
  \item Python packaging
  \item Pytest
  \item LaTeX
  \item Sphinx
  \item Linux
  \item Vim
  \item Perforce
  \item JIRA
  \item Jenkins
  \item Agile
  \item Test-driven development
  \item Elastic stack
  \end{cventryskills}

  %---------------------------------------------------------
  \cvline%
  {Air Sciences, Inc.} % Organization
  {Network Administrator (intern \& part-time)} % Job title
  %{Golden, Colorado} % Location
  {November 2011 \-- March 2014} % Date(s)
  %{%
  %  \begin{cvitems} % Description(s) of tasks/responsibilities
  %  \item {Purchased, set up, and maintained servers, laptops, and
  %    networks for a 50 person company.}
  %  \item {Introduced new processes such as a ticketing system, wiki,
  %    and KVM virtual machines \-- providing continuity and a knowledge base.}
  %  \item {Interviewed and trained three new administrators \--
  %      utilizing the wiki to create reusable materials to accelerate
  %    the new hire process going forward.}
  %  \end{cvitems}
  %}
  %\begin{cventryskills}
  %\item Django
  %\item Git
  %\item Mediawiki
  %\item Network configuration
  %\item Linux administration
  %\item User support
  %\end{cventryskills}

  %---------------------------------------------------------
  \cvline%
  {CSM Alumni Association} % Organization
  {Software Developer \-- Website, newsletter, graphics, audio,
  video} % Job description
  {August 2010 \-- April 2014} % Date(s)
  %\begin{cventryskills}
  %  \item Wordpress
  %  \item PHP
  %  \item HTML \& CSS
  %  \item Audacity audio editing
  %  \item GIMP image manipulation
  %  \item Web design
  %\end{cventryskills}
  %---------------------------------------------------------
\end{cventries}
